DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
replaced Figure by Fig. throughout the paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The first approach, presented in Figure~\ref{fig:CEGIS-precision-increment}, 
uses a multi-staged verification process. 
It starts by devising a digital controller that stabilizes the model while remaining safe for a
pre-selected time horizon ($k$) and a single initial state; then, it
employs a multi-staged verification process as follows:
(i) The first verification stage checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage 
 restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller 
$K$~\cite{abatecav2017}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
model such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.

@@

Instead of unfolding the dynamics, the second approach (shown in Figure~\ref{fig:CEGARIS}) 
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to 
simultaneously evaluate all possible progressions of the model. This eliminates the need for
a completeness threshold, since the time horizon considered in abstract acceleration is infinite.
An additional preprocessing phase is used to compute 
a set of initial bounds on $K$ based on input constraints. 
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
%
Since this model is based on abstraction, we initially perform the synthesis over a basic
model that abstracts away the complexity of the specification and is only refined to a more
complex model when a counterexample is found. 
% Thus, we may only look at the gain of the
% model to synthesise a controller and to add further restrictions on specific sections of the reach
% tube when these prove to invalidate the solution.
The use of this Counterexample-Guided 
Abstraction-Refinement results in much faster synthesis and verification since it is applied to
both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.

@@

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
namely poles must have the modulus less than one. In order to compute the poles for the digital 
system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
to achieve a general equation regarding the transfer function representation as shown in Figure~\ref{combine-controller-plant}.

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = series(controller,plant)
>> sys =
>> 
>>      0.06863 z^4 - 0.006591 z^3 - 0.01324 z^2
>>  ------------------------------------------------
>>  z^4 - 1.129 z^3 + 0.4981 z^2 - 0.8704 z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system using the series configuration (as shown in Figure~\ref{fig:typical-control-system}).}
\label{combine-controller-plant}
\end{figure}

@@

For the stability check, if any root of the polynomial $D(z)$ in Equation~\ref{equation_general} 
has modulus equal or greater than one, then the system is unstable; 
otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Figure~\ref{roots-of-dz}, 
which means that DSSynth has synthesized a stable digital controller.

>>>>

The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
uses a multi-staged verification process. 
It starts by devising a digital controller that stabilizes the model while remaining safe for a
pre-selected time horizon ($k$) and a single initial state; then, it
employs a multi-staged verification process as follows:
(i) The first verification stage checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage 
 restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller 
$K$~\cite{abatecav2017}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
model such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.

@@

Instead of unfolding the dynamics, the second approach (shown in Fig.~\ref{fig:CEGARIS}) 
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to 
simultaneously evaluate all possible progressions of the model. This eliminates the need for
a completeness threshold, since the time horizon considered in abstract acceleration is infinite.
An additional preprocessing phase is used to compute 
a set of initial bounds on $K$ based on input constraints. 
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
%
Since this model is based on abstraction, we initially perform the synthesis over a basic
model that abstracts away the complexity of the specification and is only refined to a more
complex model when a counterexample is found. 
% Thus, we may only look at the gain of the
% model to synthesise a controller and to add further restrictions on specific sections of the reach
% tube when these prove to invalidate the solution.
The use of this Counterexample-Guided 
Abstraction-Refinement results in much faster synthesis and verification since it is applied to
both phases, allowing for faster results whilst maintaining soundness for an infinite time horizon.

@@

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
namely poles must have the modulus less than one. In order to compute the poles for the digital 
system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
to achieve a general equation regarding the transfer function representation as shown in Fig.~\ref{combine-controller-plant}.

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = series(controller,plant)
>> sys =
>> 
>>      0.06863 z^4 - 0.006591 z^3 - 0.01324 z^2
>>  ------------------------------------------------
>>  z^4 - 1.129 z^3 + 0.4981 z^2 - 0.8704 z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system using the series configuration (as shown in Fig.~\ref{fig:typical-control-system}).}
\label{combine-controller-plant}
\end{figure}

@@

For the stability check, if any root of the polynomial $D(z)$ in Equation~\ref{equation_general} 
has modulus equal or greater than one, then the system is unstable; 
otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Fig.~\ref{roots-of-dz}, 
which means that DSSynth has synthesized a stable digital controller.
